True versus apparent shapes of bow shocks

### 2017-11-30 papers/Paper1/sec-conclusions.tex
More about the simulations - develop plan for using Meyers 2017
Write fig caption for simulation departure function graphs

>>>>

\section{More realistic bow shock models}
\label{sec:more-realistic-bow}

\begin{figure}
  (a)\\
  \includegraphics[width=\linewidth]
  {figs/depart-cheby-M17-MHD2040-AllB7}\\[-\baselineskip]
  (b)\\
  \includegraphics[width=\linewidth]
  {figs/depart-cheby-M17-HD2040}\\[-\baselineskip]
  \caption{Departure function for the shape of the contact
    discontinuity, measured from two numerical simulations of a
    \(20\,M_\odot\) main-sequence star, moving at \SI{40}{km.s^{-1}}
    through a uniform medium of density \SI{0.57}{cm^{-3}}
    \citep{Meyer:2017a}. (a)~Magnetohydrodynamic simulation with
    ambient magnetic field of strength \SI{7}{\micro G}, oriented
    parallel to the stellar velocity. (b)~Hydrodynamic simulation with
    zero magnetic field.  Blue dots show the measured shape, while the
    thick, pale-red line shows a 12th-order Chebyshev polynomial fit.
    The published shapes only extend to
    \(\theta \approx 130\)--\(150^\circ\), so we extrapolate the shapes out to
    \(\theta = 180^\circ\). Two different extrapolations are shown,
    corresponding to bows that are asymptotically closed (dashed red
    line) or open (solid red line).  For comparison, black lines show
    the departure function for wilkinoid (thick line) and cantoids
    (thin lines).}
  \label{fig:sim-depart}
\end{figure}

The assumptions underlying the models of the previous section may
break down in various ways.  To test whether

Most importantly, the shocked shell may not be thin.

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/test_xyprime_simulation}
  \caption{Projected shapes of contact discontinuity from simulations.}
  \label{fig:sim-xyp}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/m17-planitude-alatude}
  \caption{Apparent projected shapes of simulations.}
  \label{fig:sim-Pi-Lambda}
\end{figure}

### 2017-11-30 papers/Paper1/sec-obs-conclusions.tex
Get some screenshots together for Meyer (2016) simulations
Still need to measure arcs in ds9
Write fig caption for simulation departure function graphs

>>>>

Difference in SEDs between FIR and MIR samples?  \citet{Meyer:2016a}
say emission peaks at 3--50 micron for O star bow shocks.

Al other things being equal, larger bows will be at higher
inclinations (we should estimate how much variation in size we should
get due to inclination -- it will be more for flatter bows).  Higher
inclinations means less variation from the standing wave oscillations,
which goes against our result that larger bows have greater dispersion
in \(\Lambda'\).  Although the standing waves mainly give dispersion in
\(\Pi'\) anyhow.
